Elo World,

### 2019-03-11 trunk/chess/papers/weak.tex
Experiment to predict legal moves. Packed representation of moves. Mode for tournament where we only compute one row/col. Add stockfish node option and Stockfish1M player
start writing 'weak'

% Dramatic failure of the "suicide king" strategy against
% CCCP.
1. d4 g5 2. Bxg5 Nc6 3. Bxe7 Kxe7 4. d5 Kd6
5. dxc6+ Kc5 6. Qd6+ Kc4 7. e4#

@@

@@

// citation for knights distance:
// Counting the Number of Squares Reachable in k
// Knight's Moves
// Amanda M. Miller, David L. Farnsworth
// Open Journal of Discrete Mathematics, 2013, 3, 151-154
// http://dx.doi.org/10.4236/ojdm.2013.33027

>>>>

% [computermodern], 
\documentclass[numbers]{sigplanconf}

\usepackage{url}
% \usepackage{code}
% \usepackage{cite}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{chessboard}

% \usepackage{chessfs}
\usepackage{adjustbox}

% Define black versions of pieces for inline use. Gross, but it works.
\newcommand{\Pawn}[1][1.3ex]{%
\adjustbox{Trim=4.3pt 2.6pt 4.3pt 0pt,width=#1,margin=0.2ex 0ex 0.2ex 0ex}{\BlackPawnOnWhite}%
}%
\newcommand{\Rook}[1][1.58ex]{%
\adjustbox{Trim=3.2pt 2.2pt 3.2pt 0pt,width=#1,raise=0ex,margin=0.1ex 0ex 0.1ex 0ex}{\BlackRookOnWhite}%
}%
\newcommand{\Knight}[1][1.85ex]{%
\adjustbox{Trim=2.3pt 2.35pt 2.5pt 0pt,width=#1,raise=-0.03ex,margin=0.14ex 0ex 0.14ex 0ex}{\BlackKnightOnWhite}%
}%
\newcommand{\Bishop}[1][1.79ex]{%
\adjustbox{Trim=2.3pt 2pt 2.3pt 0pt,width=#1,raise=-0.12ex,margin=0.1ex 0ex 0.1ex 0ex}{\BlackBishopOnWhite}%
}%
\newcommand{\Queen}[1][2.05ex]{%
\adjustbox{Trim=1.2pt 2.2pt 1.2pt 0pt,width=#1,raise=-0.08ex,margin=0.1ex 0ex 0.1ex 0ex}{\BlackQueenOnWhite}%
}%
\newcommand{\King}[1][1.95ex]{%
\adjustbox{Trim=2pt 2pt 2pt 0pt,width=#1,raise=-0.06ex,margin=0.13ex 0ex 0.13ex 0ex}{\BlackKingOnWhite}%
}%

\interfootnotelinepenalty=0

% lets me explicitly set a. or 1. etc. as enum label
\usepackage{enumitem}

\pagestyle{empty}

\usepackage{ulem}
% go back to italics for emphasis, though
\normalem

\usepackage{natbib}

\setlength{\footnotesep}{2em}

% \newcommand\comment[1]{}
\newcommand\sfrac[2]{\!{}\,^{#1}\!/{}\!_{#2}}

\begin{document}

\conferenceinfo{SIGBOVIK~2019}{April 1, 2019, Pittsburgh, Pennsylvania, USA}
\copyrightyear{2019}
\title{Elo World,}
\subtitle{a framework for benchmarking weak chess engines}
\authorinfo{Dr. Tom Murphy VII Ph.D.}{tom7.org Foundation}{tom7@tom7.org}
\toappear{
Copyright \copyright\ 2019 the Regents of the Wikiplia Foundation.
Appears in SIGBOVIK 19119 with the
%
insufficient material 
%
of the Association for Computational Heresy; {\em IEEEEEE!}
press, Verlag-Verlag volume no.~0x40-2A. 1600 rating points}

\ccsdesc[500]{Evaluation methodologies~Tournaments}
\ccsdesc[500]{Chess~Being bad at it}
% \ccsdesc[100]{Software and its engineering~Control structures}
% \ccsdesc[300]{Theory of computation~Control primitives}

\terms
pawn, horse, bishop, castle, queen, king
\keywords
chess, bad

\setchessboard{showmover=false}

\newcommand\checkmate{\hspace{-.05em}\raisebox{.4ex}{\tiny\bf ++}}

\renewcommand\th{\ensuremath{{}^{\textrm{th}}}}
\newcommand\st{\ensuremath{{}^{\textrm{st}}}}
\newcommand\rd{\ensuremath{{}^{\textrm{rd}}}}
\newcommand\nd{\ensuremath{{}^{\textrm{nd}}}}
\newcommand\at{\ensuremath{\scriptstyle @}}

\date{1 April 2019}

\maketitle \thispagestyle{empty}

Fiddly bits aside, it is a solved problem to maintain a numeric rating
of players for some game (for example chess, but also sports,
e-sports, probably also z-sports if that's a thing). Though it has
some competition (suggesting the need for a meta-rating system to
compare them), the Elo Rating System~\cite{elo1978rating} is a simple
and effective way to do it.

The gist of this system is to track a score for each player. The
scores are defined such that the expected outcomes of games can
be computed from the scores (for example, a player with a rating
of 2400 should win 9/10 of her games against a player with a
rating of 2000). If the true outcome doesn't match the

.. so we can just leave it at that

% Names:
% "Stalemate"
% "Weaksauce"
% "back rank"
% "blunder"
% something with ..elo..   "elo world"
% inFIDElity
% blunderbuss
%

Interpolation, like Scoville scale.

% Dramatic failure of the "suicide king" strategy against
% CCCP.
1. d4 g5 2. Bxg5 Nc6 3. Bxe7 Kxe7 4. d5 Kd6
5. dxc6+ Kc5 6. Qd6+ Kc4 7. e4++

@@

% worstfish (black) somehow beating suicide king
% white forces the mate. Note that worstfish
% does assume its opponent will pick good moves...
1. Nf3 g5 2. b4 Na6 3. Nxg5 Nc5 4. b5 f6
5. c4 Na6 6. Nf7 Rb8 7. d3 h6 8. Kd2 Nb4
9. Kc3 Rh7 10. Kd4 Rg7 11. Kc5 Nd5 12. Nxh6 Nb4
13. Na3 Rg3 14. Qc2 Bg7 15. f4 a6 16. Qb1 Bh8
17. Qb2 f5 18. Qf6 Rxg2 19. Qh4 Rxe2 20. Bg2 e5
21. Bd2 Bf6 22. Nf7 Bh8 23. Qf2 c6 24. Kd6 Re4
25. h4 Qc7+ 26. Kxc7 Nxa2 27. Raf1 c5 28. Nh6 Ke7
29. Qd4 Ke6 30. Rc1 Bg7 31. Be1 Ra8 32. Rc2 Nc3
33. Ra2 Ne7 34. Qxe4 Bf8 35. Kd8 Nxb5 36. Qxf5+ Kd6
37. Qxd7+ Bxd7++

% Fate-based algorithms.
% The deterministic version is fairly boring, since the
% highest probability states are similar to the starting
% position (this might not be true for "survivalist"
% or "fatalist"? check?)

% weighted random is almost the same as random, because
% the weights tend to be very similar when treated
% additively. They perform slightly different from
% random, as so (101.5 million games):

%  player	elo	w/l/d
%  dangerous	986.29	1374577/1501526/15683897
%  popular	997.34	1360053/1502995/15696952
%  random_move	1000.79	1540798/1337668/15681534
%  rare	1005.85	1554600/1326707/15678693
%  safe	1009.72	1341030/1502162/15716808

% then with normalization:
%  player	elo	w/l/d
%  popular	990.93	25756/43561/346683
%  safe	993.49	28082/40769/347149
%  dangerous	996.60	30063/37451/348486
%  rare	1005.82	50656/27390/337954
%  random_move	1013.15	41747/27133/347120

@@

\nocite{elo1978rating}
\nocite{topple}
// citation for knights distance:
\nocite{miller2013counting}

\bibliography{chess}{}
\bibliographystyle{plain}

\end{document}
